Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-12 paper/disc20clustering.tex
Intro to ALG3

The proposed algorithm is a modified version of the algorithm DET proposed by Avin et al.~\cite{repartition-disc}, that for $k=3$ is $O(\ell^2)$-competitive.
In our algorithm, we choose the closest partition after a component merge instead of an arbitrary one.
This allows to bound the cost of repartition by a constant (Lemma~\ref{lem:1req}).

>>>>

The algorithm analyzed in this section is a modified version of the algorithm DET proposed by Avin et al.~\cite{repartition-disc}, that for $k=3$ is $O(\ell^2)$-competitive.
In our algorithm, we choose the closest partition after a component merge instead of an arbitrary one.
This allows to bound the cost of repartition by a constant (Lemma~\ref{lem:1req}).
